### 2014-08-21 fundamentals/intro.tex
removed reference to agent-based. We can address that previous work later.

Historically, nuclear fuel cycle simulators have addressed this with software 
ranging from spreadsheet driven flow calculators to very high-fidelity 
industrial models. To date, current tools are either static, fleet-based, or 
privately distributed. An alternative to these approaches is a dynamic, 
agent-based simulator with an open platform.

@@

Methods for calculating those metrics vary among simulators. Some model the fuel cycle at static equillibrium, while others 
capture fuel cycle dynamics.  Similarly, while some simulators discretely model 
material and and facilities, others track streams of materials and 
fleets of facilities in an aggregated fashion. Depending on their intended use, 
simulators often model some aspect of the fuel cycle in great detail. For this 
reason, simulators specialize in economics, material isotopics, or 
transmutation detail, where others do not. Some tools have even attempted 
agent-based functionality.

@@

<modified-open-source collaboration diagram>

>>>>

% MJG - I'm hesitant about using the phrase 'full detail'. I think we can be
% more precise.

Historically, nuclear fuel cycle simulators have addressed this with software 
ranging from spreadsheet driven flow calculators to full detail industrial 
models. To date, current tools are either static, fleet-based, or 
privately distributed. An alternative to these approaches is a dynamic, 
agent-based simulator with an open platform.

@@

Methods for calculating those metrics vary among simulators. Some model the fuel cycle at static equillibrium, while others 
capture fuel cycle dynamics.  Similarly, while some simulators discretely model 
material and and facilities, others track streams of materials and 
fleets of facilities in an aggregated fashion. Depending on their intended use, 
simulators often model some aspect of the fuel cycle in great detail. For this 
reason, simulators specialize in economics, material isotopics, or 
transmutation detail, where others do not.

@@

% man that figure has gone quite a ways =)
<modified-open-source collaboration diagram>

### 2014-08-21 fundamentals/verification.tex
more content and comments added in intro, examples, impl, and verification
removed benchmark section, belongs in examples. also changed title of the verification section to qa.

\section{Verification}
% Organize this section according to major topics
% give each topic a section heading in boldface.
% try to cover the major common points :
%
% problem design
% methods of measurement
% supporting models
% supporting data
% simulations run
% results

@@

\subsection{Benchmarks}
%Inpro benchmark?
%FCO code-to-code?

A simple transition scenario recently used for a code-to-code comparison within 
the national laboratories can demonstrate the ability for Cyclus to conform to 
externally defined specifications.

>>>>

\section{Quality Assurance}
% Organize this section according to major topics
% give each topic a section heading in boldface.
% try to cover the major common points :
%
% problem design
% methods of measurement
% supporting models
% supporting data
% simulations run
% results

@@

\subsubsection{Unit Tests}

Testing individual units of 'work'.

\subsubsection{Regression Tests}

Testing identical output for each pull request.

\subsubsection{Integration Tests}

Testing aggregate answers for each pull request. Specifically, previous
simulations used in publications are integration tested to confirm their output
is maintained.
